Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment

### 2022-12-02 R/model_fcs_check.Rmd
Update FCS max.height mess up

---
title: "Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment"
author: "<b>Markus Bauer*</b> <br>"
date: "<b>`r format(Sys.time(), '%Y-%m-%d')`</b>"
output:
  github_document:
    toc: true
    toc_depth: 3
    dev: jpeg
    fig_width: 12
    fig_height: 7
---

@@

```{r, include=FALSE}
knitr::knit_hooks$set(output = function(x, options){
  if(!is.null(options$max_height)){
    paste('<pre style = "max-height:', options$max_height, '; float: left; width: 910px; overflow-y: auto;">', x, "</pre>", sep = "")
  }else{
    x
  }

})
```

@@

```{r max_height = '100px'}
(emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
                  exposition | survey_year_fct, type = "response"))
```

@@

```{r echo = FALSE, max_height = "100px"}
sessionInfo()
```

>>>>

---
title: "Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment"
author: "<b>Markus Bauer*</b> <br>"
date: "<b>`r format(Sys.time(), '%Y-%m-%d')`</b>"
output:
  github_document:
    toc: true
    toc_depth: 3
    dev: jpeg
    fig_width: 12
    fig_height: 6
---

@@

@@

```{r max_height = "1000px"}
(emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
                  exposition | survey_year_fct, type = "response"))
```

@@

```{r echo = FALSE, max_height = "500px"}
sessionInfo()
```
